\section{127 --- Word Ladder}
Given two words ($\alpha$ and $\beta$), and a dictionary's word list $A$, find the length of shortest transformation sequence from $\alpha$ to $\beta$, such that:
\begin{itemize}
\item Only one letter can be changed at a time.
\item Each transformed word must exist in the word list. Note that begin word $\alpha$ is not a transformed word.
\end{itemize}
\paragraph{Note:}
\begin{itemize}
\item Return 0 if there is no such transformation sequence.
\item All words have the same length.
\item All words contain only lowercase alphabetic characters.
\item You may assume no duplicates in the word list.
\item You may assume $\alpha$ and $\beta$ are non-empty and are not the same.
\end{itemize}
\paragraph{Example 1:}
\begin{flushleft}
\textbf{Input}: $\alpha$ = \textbf{hit}, $\beta$ = \textbf{cog}, $A$ = (hot, dot, dog, lot, log, cog)
\\
\textbf{Output}: 5
\\
\textbf{Explanation}: As one shortest transformation is hit \textrightarrow hot \textrightarrow dot \textrightarrow dog \textrightarrow cog, return its length 5.
\end{flushleft}
\paragraph{Example 2:}
\begin{flushleft}
\textbf{Input}: $\alpha$ = \textbf{hit},  $\beta$ = \textbf{cog}, $A$ = (hot, dot, dog, lot, log)
\\
\textbf{Output}: 0
\\
\textbf{Explanation}: The end word \textit{cog} is not in $A$, therefore no possible transformation.
\end{flushleft}
\begin{CJK*}{UTF8}{gbsn}
这道题和上一题类似，但是相对简单，因为只需要求出最短路径的长度。同样是用一个hash set代表当前层的所有string，然后根据给定的规则进行变换，得到下一层的hash set，然后交换这两个hash set，使得算法能够前进到下一层，如果在变换中找到目标string即$\beta$，则返回找到的层数，也就是最短路径的长度。
\end{CJK*}
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{BFS}
\begin{algorithmic}[1]
\Procedure{LadderLength}{$\alpha, \beta, A$}
\If{$\beta \notin A$} \Comment The end word is not in the given word list
\State \Return 0
\EndIf
\State $x:=\emptyset$ \Comment $x$ is a hash set which has all strings in current level in the BFS tree
\State $x\gets x+\alpha$ \Comment The BFS tree's root is $\alpha$
\State $\ell:=0$ \Comment The length of transformation
\While{$x\neq \emptyset$}
\State $\ell\gets \ell +1$ \Comment Increment level when searching in a new level in the BFS tree
\State $y:=\emptyset$ \Comment $y$ is a hash set which has all strings transformed from words in $x$
\For{$w\in x$} \label{127for3}
\State $s:=w$
\For{$i:=0\to |s|$} \Comment Start transform process \label{127for2}
\State $c:=s[i]$ \Comment Current letter 
\For{$k:=\texttt{char}(a) \to \texttt{char}(z)$ \textbf{and} $k\neq c$} \Comment Try each lowercase letter \label{127for1}
\State $s[i]\gets k$ \Comment Do transform
\If{$s=\beta$} \Comment Reach the end word
\State \Return $\ell +1$ \Comment Need to return the number of next level
\EndIf
\State $A\gets A- s$ \Comment Remove $s$ from $A$ to avoid repeating search
\State $y\gets y+s$ \Comment Add to next level
\EndFor \Comment End[\ref{127for1}]
\State $s[i] = c$ \Comment Restore $s$
\EndFor \Comment End[\ref{127for2}]
\EndFor \Comment End[\ref{127for3}]
\State $x\gets y$ \Comment Update $x$ as next level
\EndWhile
\State \Return 0 \Comment Cannot reach end word
\EndProcedure
\end{algorithmic}
\end{algorithm}