\section{140 --- Word Break II}
Given a non-empty string $S$ and a dictionary $A$ containing a list of non-empty words, add spaces in $S$ to construct a sentence where each word is a valid dictionary word. Return all such possible sentences.
\paragraph{Note:}
\begin{itemize}
\item The same word in the dictionary may be reused multiple times in the segmentation.
\item You may assume the dictionary does not contain duplicate words.
\end{itemize}
\paragraph{Example 1:}
\begin{flushleft}
\textbf{Input}: $S$ = catsanddog, $A = [\text{cat}, \text{cats}, \text{and}, \text{sand}, \text{dog}]$
\\
\textbf{Output}:(cats and dog, cat sand dog)
\end{flushleft}
\paragraph{Example 2:}
\begin{flushleft}
\textbf{Input}: $S$ = pineapplepenapple, $A= [\text{apple, pen, applepen, pine, pineapple}]$
\\
\textbf{Output}:(pine apple pen apple, pineapple pen apple, pine applepen apple)
\\
\textbf{Explanation}: Note that you are allowed to reuse a dictionary word.
\end{flushleft}
\paragraph{Example 3:}
\begin{flushleft}
\textbf{Input}: $S = \text{catsandog}$, $A = [\text{cats, dog, sand, and, cat}]$
\\
\textbf{Output}: $\emptyset$
\end{flushleft}
\subsection{Dynamic Programming With Memeorization}
因为是要得到输出所有的组合，而不仅仅是判定是否能拆分，因此最佳的选择是采用递归式Dynamic Programming加上Memorization。由于返回的是字符串数组，因此用于Memorziation的数据结构最佳选择就是hash map，其中key是字符串，value则是该字符串所能拆分出的字符串拼成的句子字符串array。
\par
递归中具体的算法步骤如下
\begin{enumerate}
    \item 首先看当前字符串在Memo中是否存在，如果存在直接返回保存的结果。
    \item 如果当前字符串是空字符串，很明显直接返回包含空字符串的数组。
    \item 然后测试字典中的每个word，如果发现某个word和当前字符串从其起始位置开始的相同长的子字符串相等，那么就从这个word长度的下一个位置开始继续递归。然后根据递归返回的字符串数组，将其中的每个字符串加上这个word作为前缀，然后将得到的字符串数组作为以当前字符串为key的value保存到$Memo$中。
\end{enumerate}
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{DFS + Memorization}
\begin{algorithmic}[1]
\Procedure{WordBreak}{$S, L, W$}
\State Initialize $M:=\emptyset$ as the memorization hash map
\State $\texttt{ans}:=\texttt{DFS}(S, W, M)$
\EndProcedure
\end{algorithmic}
\end{algorithm}
\texttt{DFS}递归搜索可以将$S$进行分割形成的句子字符串，分割产生的word必须在给定的字典$W$中。$M$用于在递归过程中记录字符串及其对应的句子字符串数组。
\begin{algorithm}[H]
\caption{DFS Helper Function}
\begin{algorithmic}[1]
\Function{DFS}{$S, L, W, M$}
\If{$S=\emptyset$} \Comment $S$ is empty
\State \Return $[\emptyset]$ \Comment Return an array contains only one empty string
\EndIf
\If{$S\in M$} \Comment $S$ is a key in $M$
\State \Return $M[S]$ \Comment Directly return the saved result
\EndIf
\State $A:=\emptyset$ \Comment The sentense string array for current string $S$
\For{$\omega \in W$} \Comment Iterate each word $\omega$ in $W$
\State $\ell:=|\omega|$ \Comment The length of current word
\State $S_0:=S[0,\ell-1]$ \Comment The substring starting from 0
\If{$S_0=\omega$} \label{140if2}
\State $S_1:=S[\ell, L-1]$ \Comment The substring after the matched word
\State $Z:=\texttt{DFS}(S_1, L-\ell, W, M)$ \Comment Recursively get result for $S_1$ 
\For{$z\in Z$} \Comment Iterate each sentense $z$ in $Z$ \label{140for1}
\If{$z=\emptyset$} \Comment $z$ is empty \label{140if1}
\State $A\gets A + \omega$ \Comment $\omega$ is the only word in the sentence
\algstore{140algo}
\end{algorithmic}
\end{algorithm}
\begin{algorithm}[H]
\begin{algorithmic}[1]
\algrestore{140algo}
\Else
\State $t:=\omega+\text{\textvisiblespace}+z$ \Comment Add $\omega$ as the first word in $z$
\State $A\gets A + t$
\EndIf \Comment End[\ref{140if1}]
\EndFor \Comment End[\ref{140for1}]
\EndIf \Comment End[\ref{140if2}]
\EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}
