\section{153 --- Find Minimum in Rotated Sorted Array}
Suppose an array $A$ sorted in ascending order is rotated at some pivot unknown to you beforehand. (i.e., \fcj{[0,1,2,4,5,6,7]} might become  \fcj{[4,5,6,7,0,1,2]}).

Find the minimum element.

You may assume no duplicate exists in the array.
\paragraph{Example 1:}
\begin{flushleft}
\textbf{Input}: \fcj{[3,4,5,1,2]}

\textbf{Output}: 1
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: \fcj{[4,5,6,7,0,1,2]}

\textbf{Output}: 0
\end{flushleft}
\subsection{Binary Search}

基于二分搜索，假设$l$, $r$是当前搜索的边界，那么位于中间位置$m=(l+r)/2$的数$A[m]$。如果这个数比$A[r]$大，那么表明最小值出现在$A[m+1\ldots r]$区间内，如果比$A[r]$小，则最小值出现在$A[l\ldots m]$中。而题目中给出了没有重复的数字条件，因此不需要考虑$A[m]$和$A[r]$相等的情况。

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Binary Search}]
int findMin( vector<int>& A )
{
	//right boundary of searching
	int r = static_cast< int >( A.size() - 1 ); 
	//left boundary of searching
	int l = 0;

	//We need l to be a valid index 
	//so the condition is (l < r)
	//not (l<=r)
	while ( l < r )
	{
		int mid = ( l + r ) / 2;

		if ( A[mid] > A[r] )
		{
			//The minimum is in [mid+1,r]
			l = mid + 1;
		}
		else
		{
			//The minimum is in [l, mid]
			r = mid;
		}
	}

	return A[l];
}
\end{lstlisting}

\subsection{Binary Search II}
Since the array is rotated, we need a modified binary search. 

In this modified version of binary search algorithm, we are looking for a inflection point.

\begin{itemize}
\item All the elements to the left of inflection point $>$ first element of the array.
\item All the elements to the right of inflection point $<$ first element of the array.
\end{itemize}

Thus, this modified version of binary search has following steps

\begin{enumerate}
\item Find the \fcj{mid} element of the array.
\item If \fcj{mid} is larger than ($>$) first element of array, this means that we need to look for the \textit{inflection point} on the right of \fcj{mid}.
\item If \fcj{mid} is less than ($<$) first element of array, we need to look for the \textit{inflection point} on the left of \fcj{mid}.
\item We stop our search when we find the \textit{inflection point}, when either of the two conditions is satisfied:

\begin{itemize}
\item \fcj{nums[mid] > nums[mid + 1]}. Hence, \fcj{mid+1} is the smallest.
\item \fcj{nums[mid - 1] > nums[mid]}. Hence, \fcj{mid} is the smallest.
\end{itemize}
\end{enumerate}

\begin{lstlisting}[style=customc, caption={Binary Search II}]
int findMin( vector<int>& nums )
{
    if( nums.size() == 1 )
    {
        return nums[0];
    }
    if( nums.back() > nums[0] )
    {
        //the array is not rotated
        return nums[0];
    }
    int l = 0;
    int r = static_cast< int >( nums.size() - 1 );
    while( l <= r )
    {
        int mid = ( l + r ) / 2;
        if( nums[mid] > nums[mid + 1] )
        {
            //mid+1 is the inflection point
            return nums[mid + 1];
        }
        if( nums[mid] < nums[mid - 1] )
        {
            //mid is the inflection point
            return nums[mid];
        }
        if( nums[mid] > nums[0] )
        {
            //inflection point lies right side of mid
            l = mid + 1;
        }
        else
        {
            //inflection point lies left side of mid
            r = mid - 1;
        }
    }
    return -1;
}
\end{lstlisting}
