\section{166 --- Fraction to Recurring Decimal}
Given two integers $N$ and $D$ representing the numerator and denominator of a fraction, return the fraction in string format.
\par
If the fractional part is repeating, enclose the repeating part in parentheses.
\paragraph{Example 1:}
\begin{flushleft}
\textbf{Input}: $N = 1$, $D = 2$
\\
\textbf{Output}: $0.5$
\end{flushleft}
\paragraph{Example 2:}
\begin{flushleft}
\textbf{Input}: $N = 2$, $D = 1$
\\
\textbf{Output}: 2
\end{flushleft}
\paragraph{Example 3:}
\begin{flushleft}
\textbf{Input}: $N = 2$, $D = 3$
\\
\textbf{Output}: $0.(6)$
\end{flushleft}
\subsection{Hash Map}
\begin{itemize}
    \item 当余数发生重复时，即可停止计算，因为已经找到循环点了。
    \item 用一个hash map保存每个小数位上的数字。
    \item 由于要算出小数每一位，因此和手动计算一样，每次要把余数乘10，再除以denominator，得到的商即为小数的下一位数字。
    \item 如果余数在之前出现过，则在这个余数之前对应的位置前加左括号，然后在当前位置处加右括号。
\end{itemize}
另外还需要考虑如下几个边界情况
\begin{itemize}
    \item 需要注意符号是否为正或者负。
    \item 可能会造成 overflow 的情况，比如 $N = -2147483648$, $D = -1$，因此具体算法实现时应使用比int type更长的类型，比如long long。
    \item 如果结果为0，而其中一个数字是负数，也要注意不能把负号放入结果中。
\end{itemize}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Mathematical}]
string fractionToDecimal( int numerator, int denominator )
{
    //1. check if the result will be negative or not
    unsigned char flag = 0;
    auto ne = static_cast<long long>( numerator );
    if( numerator < 0 )
    {
        ++flag;
        ne = -ne;
    }
    auto de = static_cast<long long>( denominator );
    if( denominator < 0 )
    {
        ++flag;
        de = -de;
    }
    string ans;
    if( flag == 1 )
    {
        //result will be negative
        //add minus symbol
        ans.push_back( '-' );
    }
    //2. get the integer part
    auto q = ne / de;
    auto r = ne - q * de;
    ans += to_string( q );
    if( r == 0 )
    {
        //no decimal part
        if( q == 0 )
        {
            //we may get "-0"
            //so return "0" here
            return "0";
        }
        return ans;
    }
    //3.add decimal part
    ans.push_back( '.' );
    //record the repeat part
    unordered_map<long long, size_t> memo;
    while( r != 0 )
    {
        auto it = memo.find( r );
        if( it != memo.end() )
        {
            //we found the recurrent part
            //add parenthesis
            ans.insert( it->second, "(" );
            ans.push_back( ')' );
            break;
        }
        //each decimal map to a position in ans
        memo.emplace( r, ans.size() );
        //get more decimals
        r *= 10;
        q = r / de;
        ans += to_string( q );
        r = r - de * q;
    }
    return ans;
}
\end{lstlisting}