\section{174 --- Dungeon Game}
The demons had captured the princess ($P$) and imprisoned her in the bottom-right corner of a dungeon. The dungeon consists of $M \times N$ rooms laid out in a 2D grid $D$. Our valiant knight ($K$) was initially positioned in the top-left room and must fight his way through the dungeon to rescue the princess.
\par
The knight has an initial health point represented by a positive integer. If at any point his health point drops to 0 or below, he dies immediately.
\par
Some of the rooms are guarded by demons, so the knight loses health (negative integers) upon entering these rooms; other rooms are either empty (0's) or contain magic orbs that increase the knight's health (positive integers).
\par
In order to reach the princess as quickly as possible, the knight decides to move only rightward or downward in each step.
\par
\textbf{Write a function to determine the knight's minimum initial health so that he is able to rescue the princess}.
\par
For example, given the dungeon below, the initial health of the knight must be at least 7 if he follows the optimal path \textbf{RIGHT} \textrightarrow \textbf{RIGHT} \textrightarrow \textbf{DOWN} \textrightarrow \textbf{DOWN}.


\begin{figure}[H]
\begin{tikzpicture}[square/.style={draw=#1, minimum size=1.5cm,anchor=south west}]
\matrix(m)[matrix of nodes, nodes={square=gray!20!}, column sep=0pt, row sep=0pt]
{
 $-2(K)$  & $-3$  & 3 \\
 $-5$  & $-10$  & 1 \\
 $10$  & $30$  & $-5(P)$ \\
};
\draw[line width=1pt] (m-1-1.north west) rectangle (m-3-3.south east);
\end{tikzpicture}
\end{figure}
\paragraph{Note:}
\begin{itemize}
\item The knight's health has no upper bound.
\item Any room can contain threats or power-ups, even the first room the knight enters and the bottom-right room where the princess is imprisoned.
\end{itemize}
\subsection{Backward Dynamic Programming}
\begin{CJK*}{UTF8}{gbsn}
\begin{itemize}
\item knight在每个格子的生命值至少为1
\item 从$P$的位置回溯进行DP。
\end{itemize}
\end{CJK*}
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{}
\begin{algorithmic}[1]
\Procedure{CalculateMinimumHP}{$D, R, C$}
\State $\star$ Create a 2D array $F$ same dimensions as $D$
\State $F[R-1][C-1] \gets \max(1, 1 - D[R-1][C-1])$ \Comment At least the knight must have 1 health point
\State $\star$ Fill last column of $F$
\For{$r:=R-2 \to 0$}
\State $F[r][C-1]\gets\max(1, F[r+1][C-1] - D[r][C-1])$
\EndFor
\State $\star$ Fill last row of $F$
\For{$c:=C-2 \to 0$}
\State $F[R-1][c]\gets\max(1, F[R-1][c+1] - D[R-1][c])$
\EndFor
\State $\star$ Filling all remaining cells back to $F[0][0]$
\For{$r:=R-2 \to 0$}
\For{$c:=C-2 \to 0$}
\State $x:=\min(F[r+1][c], F[r][c+1])$ \Comment Get minimum required health points
\State $\star$ $x-D[r][c]$ is the health points required to move to \textbf{RIGHT} or \textbf{DOWN}
\State $\star$ But knight must have at least 1 health point
\State $F[r][c]\gets\max(1, x - D[r][c])$ 
\EndFor
\EndFor
\State \Return $F[0][0]$
\EndProcedure
\end{algorithmic}
\end{algorithm}
\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Source Code}]
int calculateMinimumHP( vector<vector<int>>& dungeon )
{
    int rows = static_cast<int>( dungeon.size() );
    int cols = static_cast<int>( dungeon[0].size() );
    vector<vector<int>> F( rows, vector<int>( cols, 0 ) );

    F[rows - 1][cols - 1] = ( max )( 1, 1 - D[rows - 1][cols - 1] );

    for( int r = rows - 2; r >= 0; --r )
    {
        F[r][cols - 1] = ( max )( 1, F[r + 1][cols - 1] - dungeon[r][cols - 1] );
    }

    for( int c = cols - 2; c >= 0; --c )
    {
        F[rows - 1][c] = ( max )( 1, F[rows - 1][c + 1] - dungeon[rows - 1][c] );
    }

    for( int r = rows - 2; r >= 0; --r )
    {
        for( int c = cols - 2; c >= 0; --c )
        {
            int next = ( min )( F[r + 1][c], F[r][c + 1] );
            F[r][c] = ( max )( 1, next - dungeon[r][c] );
        }
    }

    return F[0][0];
}
\end{lstlisting}