\section{198 --- House Robber}
You are a professional robber planning to rob houses along a street. Each house has a certain amount of money stashed, the only constraint stopping you from robbing each of them is that adjacent houses have security system connected and it will automatically contact the police if two adjacent houses were broken into on the same night.
\par
Given a list of non-negative integers $A$ representing the amount of money of each house, determine the maximum amount of money you can rob tonight without alerting the police.
\paragraph{Example 1:}
\begin{flushleft}
\textbf{Input}: $[1,2,3,1]$
\\
\textbf{Output}: 4
\\
\textbf{Explanation}: 
\\
Rob house 1 (money = 1) and then rob house 3 (money = 3). Total amount you can rob $= 1 + 3 = 4$.
\end{flushleft}
\paragraph{Example 2:}
\begin{flushleft}
\textbf{Input}: $[2,7,9,3,1]$
\\
\textbf{Output}: 12
\\
\textbf{Explanation}:
\\
Rob house 1 (money = 2), rob house 3 (money = 9) and rob house 5 (money = 1). Total amount you can rob $= 2 + 9 + 1 = 12$.

\end{flushleft}   
\subsection{Dynamic Programming}
\begin{CJK*}{UTF8}{gbsn}
分别用$X[i]$ 和 $Y[i]$表示当选择和不选择$A[i]$时，所能得到的最大amount。相应的递推公式为
\begin{itemize}
\item $X[i]\gets\max(X[i-1], Y[i-1] + A[i])$：因为选择了$A[i]$就不能选择$A[i-1]$。
\item $Y[i]\gets\max(X[i-1], Y[i-1])$：如果不选择$A[i]$，可以选择$A[i-1]$
\end{itemize}
可以看出$X[i]$，$Y[i]$仅仅取决于$X[i-1]$和$Y[i-1]$，因此可以用四个变量$\alpha$，$\beta$，$x$和$y$分别代表$X[i-1]$，$Y[i-1]$，$X[i]$和$Y[i]$。
\end{CJK*} 
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{Dynamic Programming}
\begin{algorithmic}[1]
\Procedure{Rob}{$A, L$}
\State $\star$ Check if $A$ is empty
\If{$L=0$}
\State \Return 0
\EndIf
\State $\star$ Initialize the dynamic programming states
\State $x:=A[0]$ \Comment When $A[0]$ is selected, $X[0]=A[0]$
\State $y:=0$ \Comment When $A[0]$ is not selected, $Y[0]=0$
\State $\star$ Start the iterative process
\For{$i:=1\to L-1$}
\State $\alpha:=x$ \Comment Save $X[i-1]$ to $\alpha$
\State $\beta:=y$ \Comment Save $Y[i-1]$ to $\beta$
\State $x\gets (max)(x, \beta+A[i])$
\State $y\gets (max)(y, \alpha)$
\EndFor
\State \Return $\max(x,y)$ \Comment The maximum of $X[L-1]$ and $Y[L-1]$ is the result
\EndProcedure
\end{algorithmic}
\end{algorithm}        
\setcounter{lstlisting}{0}
\begin{mdframed}[style=mymdf]
\begin{lstlisting}[style=customc, caption={Dynamic Programming}]
int rob( vector<int>& nums )
{
    if( nums.empty() )
    {
        return 0;
    }

    int x = nums[0];
    int y = 0;

    for( size_t i = 1; i < nums.size(); ++i )
    {
        int cur_x = ( max )( x, y + nums[i] );
        int cur_y = ( max )( y, x );

        x = cur_x;
        y = cur_y;
    }

    return ( max )( x, y );
}
\end{lstlisting} 
\end{mdframed}
