\section{350 --- Intersection of Two Arrays II}
Given two arrays $ A $ and $ B $, write a function to compute their intersection.

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}:$  A = [1,2,2,1] $,$  B = [2,2] $
\\
\textbf{Output}: [2]
\end{flushleft}


\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: $ A = [4,9,5] $, $ B = [9,4,9,8,4] $
\\
\textbf{Output}: [9,4]
\end{flushleft}

\paragraph{Note:}

\begin{itemize}
\item Each element in the result should appear as many times as it shows in both arrays.
\item The result can be in any order.
\end{itemize}

\paragraph{Follow up:}

\begin{itemize}
\item What if the given array is already sorted? How would you optimize your algorithm?
\item What if $ A $'s size is small compared to $ B $'s size? Which algorithm is better?
\item What if elements of $ B $ are stored on disk, and the memory is limited such that you cannot load all elements into the memory at once?
\end{itemize}

\subsection{Hash Map}
\begin{itemize}
\item 这道题是 349 --- Intersection of Two Arrays的拓展，不同之处在于这道题允许我们在intersection中加入重复的数字，而且是尽可能多的加入，而349只允许重复的数字在intersection中只有一个。
\item 用一个hash map来建立$A$中字符和其出现个数之间的映射, 然后遍历$B$。如果当前字符在哈希表中的个数大于0，则将此字符加入结果中，然后将其在map中的对应值减1。
\end{itemize}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Hash Set}]
vector<int> intersect( vector<int>& nums1, vector<int>& nums2 )
{
    unordered_map<int, int> m;

    //create the map between
    //the number and its counts
    for( int n :  nums1 )
    {
        auto it = m.find( n );
        if( it == m.end() )
        {
            m.emplace( n, 1 );
        }
        else
        {
            ++it->second;
        }
    }

    vector<int> ans;

    for( int n :  nums2 )
    {
        auto it = m.find( n );

        if( it != m.end() )
        {
            //only add n
            //if the counts still larger than zero
            if( it->second > 0 )
            {
                ans.push_back( n );
                --it->second;
            }
        }
    }

    return ans;
}
\end{lstlisting}

\subsection{Sorted Arrays}
\begin{itemize}
\item 如果两个数组是sorted，那么可以用类似double pointer的方法。
\item 用$ x $和$ y $两个变量分别指向A和B的起始位置，如果$A[x]=B[y]$，那么将这个数字放入输出数组中。然后$ x $和$ y $都increments。
\item 如果$A[x]>B[y]$，则increment $ y $。反之，则increments $ x $。
\end{itemize}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Sorting}]
vector<int> intersect( vector<int>& nums1, vector<int>& nums2 )
{
    size_t x = 0;
    size_t y = 0;

    sort( nums1.begin(), nums1.end() );
    sort( nums2.begin(), nums2.end() );

    vector<int> ans;

    while( ( x < nums1.size() ) && ( y < nums2.size() ) )
    {
        if( nums1[x] == nums2[y] )
        {
            ans.push_back( nums1[x] );
            ++x;
            ++y;
        }
        else if( nums1[x] > nums2[y] )
        {
            ++y;
        }
        else
        {
            ++x;
        }
    }

    return ans;
}
\end{lstlisting}

\subsection{Follow Up}
\begin{enumerate}
\item What if elements of $B$ are stored on disk, and the memory is
limited such that you cannot load all elements into the memory at
once? --- If only $B$ cannot fit in memory, put all elements of $A$ into a hash map, read chunks from $B$ that fit into the memory, and record the intersections.
\item If both $ A $ and $ B $ are so huge that neither fit into the memory, sort them individually (external sort), then read 2 elements from each array at a time in memory, record intersections.
\end{enumerate}

\paragraph{Similar Problems}
\begin{itemize}
\item \textbf{349. Intersection of Two Arrays}
\item \textbf{1002. Find Common Characters}
\end{itemize}