\section{238 --- Product of Array Except Self}
Given an array $A$ of $n$ integers where $n > 1$,  return an array $B$ such that B[i] is equal to the product of all the elements of $A$ except $A[i]$.

\paragraph{Example:}
\begin{flushleft}
\textbf{Input}:  $[1,2,3,4]$
\\
\textbf{Output}: $[24,12,8,6]$
\end{flushleft}

\paragraph{Note:}
\begin{itemize}
\item Please solve it without division and in O(n).
\end{itemize}

\paragraph{Follow up:}
\begin{itemize}
\item Could you solve it with constant space complexity? (The output array $B$ does not count as extra space for the purpose of space complexity analysis.)
\end{itemize}
\subsection{Simplify Prefix And Postfix Product Array To Two Variables}
\begin{CJK*}{UTF8}{gbsn}
\begin{itemize}
\item 如果用prefix and postfix product array，就很简单了，从左到右逐个获得prefix product。然后再从右到左逐个获得postfix product，两个相乘就是所在index的product except itself。
\item 但其实可以将prefix and postfix product array简化成两个变量，因为我们只关心上一个值。
\end{itemize}
\end{CJK*}
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{Prefix And Postfix Products}
\begin{algorithmic}[1]
\Procedure{ProductExceptSelf}{$A, L$}
\State $\star$ Initialize $\alpha$ and $\beta$ as ones. $\alpha$ will save the prefix products while $\beta$ for postfix products.
\State $\star$ Initialize $P$ as the result array. $P$ has length $L$ and all values are initialized to 1.
\State $\ast$ Start the process of finding prefix and postfix products
\For{$i:=0$ \textbf{to} $L-1$}
\State $P[i]\gets P[i] \times \alpha$
\State $\alpha\gets \alpha\times A[i]$ \Comment Update prefix product
\State \Return $P$
\algstore{238algo}
\end{algorithmic}
\end{algorithm}
\begin{algorithm}[H]
\begin{algorithmic}[1]
\algrestore{238algo}
\State $j:=L-i-1$ \Comment We needs to get postfix product at same time
\State $P[j]\gets P[j]\times\beta$ 
\State $\beta\gets\beta\times A[j]$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\begin{CJK*}{UTF8}{gbsn}
\paragraph{Note}
\begin{itemize}
\item 上述算法中，最开始其实$P[i]$和$P[j]$都不是正确的值，但是由于我们是同时从两边进行更新，因此循环结束后就会得到正确的值。
\end{itemize}
\end{CJK*}
\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Prefix And Postfix Product}]
vector<int> productExceptSelf( vector<int>& nums )
{
    int alpha = 1;
    int beta = 1;

    vector<int> P( nums.size(), 1 );

    for( size_t i = 0; i < nums.size(); ++i )
    {
        //get prefix product
        P[i] *= alpha;
        alpha *= nums[i];

        //prcocess postfix product
        auto j = nums.size() - i - 1;
        P[j] *= beta;
        beta *= nums[j];
    }

    return P;
}
\end{lstlisting}