\section{277 --- Find the Celebrity}
Suppose you are at a party with $n$ people (labeled from 0 to $n-1$) and among them, there may exist one celebrity. The definition of a celebrity is that all the other $n-1$ people know him/her but he/she does not know any of them.
\par
Now you want to find out who the celebrity is or verify that there is not one. The only thing you are allowed to do is to ask questions like: ``Hi, A. Do you know B?'' to get information of whether $A$ knows $B$. You need to find out the celebrity (or verify there is not one) by asking as few questions as possible (in the asymptotic sense).
\par
You are given a helper function 
\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc]
bool knows(a, b)
\end{lstlisting}
which tells you whether $A$ knows $B$. Implement a function
\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc]
int findCelebrity(n)
\end{lstlisting}
your function should minimize the number of calls to \texttt{knows}.

\paragraph{Note:} 
\begin{itemize}
\item There will be exactly one celebrity if he/she is in the party. 
\item Return the celebrity's label if there is a celebrity in the party.
\item If there is no celebrity, return $-1$.
\end{itemize}
\subsection{Two Round Checking}
\begin{itemize}
\item 初始化celebrity的编号$x$为0
\item 从$1$到$n-1$调用函数\texttt{knows}，如果第$i$th个人\texttt{knows}$(x,i)$是\texttt{true}，那么更新$x$为$i$。因为只有一个celebrity，因此这个过程能够找到可能的celebrity。
\item 在从$0$到$n-1$循环来检查$x$是否为celebrity，只要发现任何一个$i$使得\texttt{knows}$(x,i)$为\texttt{true}(即$x$ knows $i$)，或者\texttt{knows}$(i,x)$为\texttt{false}(即$i$不认识$x$)，那么表示$x$并不是celebrity。
\end{itemize}
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{Two Round Checking}
\begin{algorithmic}[1]
\Procedure{FindCelebrity}{$n$}
\State $x:=0$
\State $ast$ 找到可能的celebrity。
\For{$i:=1$ \textbf{to} $n-1$}
\If{\Call{knows}{$x,i$} is \texttt{true}} \Comment $x$ knows $i$ so $x$ cannot be celebrity
\State $x\gets i$ \Comment Update $x$ to $i$ because $i$ is the possible celebrity
\EndIf
\EndFor
\State $\ast$ 检查$x$是否为celebrity
\For{$i:=0$ \textbf{to} $n-1$}
\If{$i\neq x$}
\If{\Call{knows}{$x,i$} is \texttt{true}}
\State \Return $-1$ \Comment $x$ knows $i$ so $x$ cannot be the celebrity
\EndIf
\If{\Call{knows}{$i,x$} is \texttt{false}}
\State \Return $-1$ \Comment $i$ does not know $x$ so $x$ cannot be the celebrity
\EndIf
\EndIf
\EndFor
\State \Return $x$ \Comment $x$ is the celebrity
\EndProcedure
\end{algorithmic}
\end{algorithm}
\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Two Round Checking}]
int findCelebrity( int n )
{
    int x = 0;

    //find the possible celebrity
    for( int i = 0; i < n; ++i )
    {
        if( knows( x, i ) )
        {
            x = i;
        }
    }
    for( int i = 0; i < n; ++i )
    {
        if( x != i && ( knows( x, i ) || !knows( i, x ) ) )
        {
            //either x knows someone
            //or someone does not know x
            //x cannot be the celebrity
            return -1;
        }
    }
    return x;
}
\end{lstlisting}