\section{296 --- Best Meeting Point}
A group of two or more people wants to meet and minimize the total travel distance. You are given a 2D grid of values 0 or 1, where each 1 marks the home of someone in the group. The distance is calculated using Manhattan Distance, where distance$(p_1, p_2) = \lvert p_2.x - p_1.x\rvert + \lvert p_2.y - p_1.y \rvert$.
\par
For example, given three people living at $(0,0)$, $(0,4)$, and $(2,2)$:
\begin{table}[H]
\begin{tabular}{ccccc}
1 & 0 & 0 & 0 & 1\\
0 & 0 & 0 & 0 & 0\\
0 & 0 & 1 & 0 & 0
\end{tabular}
\end{table}
The point $(0,2)$ is an ideal meeting point, as the total travel distance of $2+2+2=6$ is minimal. So return 6.

\paragraph{Hint:}

\begin{itemize}
\item Try to solve it in one dimension first. How can this solution apply to the two dimension case?
\end{itemize}
\subsection{Sorting}
根据题目中的提示，先从一维的情况分析，假设只有两个点$A$和$B$，那么显然最佳的meeting点$P$肯定是在$A$和$B$之间，而$A$和$B$中间任何一点到$A$和$B$的距离之和就是$A$和$B$的距离。
\begin{figure}[H]
\begin{tikzpicture}
[mynode/.style={draw,circle,minimum size=5mm, fill=gray!20!}]
\node(){};
\node[mynode](1) {$A$};
\node[mynode](2) [right = 2mm of 1] {$P$};
\node[mynode](3) [right = 4mm of 2] {$B$};
\draw (1) -- (2);
\draw (2) -- (3);
\end{tikzpicture}
\end{figure}

如果在$A$，$B$之外再加两个点$C$和$D$：

\begin{figure}[H]
\begin{tikzpicture}
[mynode/.style={draw,circle,minimum size=5mm, fill=gray!20!}]
\node(){};
\node[mynode](1) {$C$};
\node[mynode](2) [right = 8mm of 1] {$A$};
\node[mynode](3) [right = 2mm of 2] {$P$};
\node[mynode](4) [right = 4mm of 3] {$B$};
\node[mynode](5) [right = 8mm of 4] {$D$};
\draw (1) -- (2);
\draw (2) -- (3);
\draw (3) -- (4);
\draw (4) -- (5);
\end{tikzpicture}
\end{figure}
同样，最佳meeting点$P$点的位置还是在$[A, B]$内，这时$P$到$A$，$B$，$C$，$D$和四个点的距离之和即为$A$和$B$之间的距离加上$C$和$D$之间的距离，
\par
\begin{itemize}
    \item 将所有1的点的$x$和$y$的坐标分别放入两个数组中，然后排序这两个数组。
    \item 对每个数组，用最后一个值减去第一个值，就是最外围两个点之间的距离，然后倒数第二个值减去第二个值，以此类推，直到最中间停止。
    \item 累加这些距离值就分别是$x$和$y$方向上的最短距离和。由于题目中要求的是曼哈顿距离，因此只要把$x$和$y$方向的距离分别计算处理，直接相加就是所要求的最短距离和了。
\end{itemize}
\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Sorting}]
int minTotalDistance( vector<vector<int>>& grid )
{
    vector<int> rows;
    vector<int> cols;

    int m = static_cast< int >( grid.size() );
    int n = static_cast< int >( grid[0].size() );

    rows.reserve( m );
    cols.reserve( n );

    for( int i = 0; i < m; ++i )
    {
        for( int j = 0; j < n; ++j )
        {
            if( grid[i][j] == 1 )
            {
                rows.push_back( i );
                cols.push_back( j );
            }
        }
    }

    int distX = minDist( rows );
    int distY = minDist( cols );

    //The distance is manhattan distance
    return distX + distY;
}

int minDist( vector<int>& pts )
{
    sort( pts.begin(), pts.end() );

    int l = 0;
    int r = static_cast< int >( pts.size() ) - 1;

    int dist = 0;

    //Find distance of each end
    while( l < r )
    {
        dist += ( pts[r] - pts[l] );
        ++l;
        --r;
    }

    return dist;
}
\end{lstlisting}