\section{9 --- Palindrome Number}
Determine whether an integer $x$ is a palindrome. An integer is a \textbf{palindrome} when it reads the same backward as forward.

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: 121
\\\
\textbf{Output}: \texttt{true}
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: $-121$
\\
\textbf{Output}: \texttt{false}
\\
\textbf{Explanation}: 
\\
From left to right, it reads $-121$. From right to left, it becomes $121-$. Therefore it is not a palindrome.
\end{flushleft}

\paragraph{Example 3:}

\begin{flushleft}
\textbf{Input}: 10
\\
\textbf{Output}: \texttt{false}
\\
\textbf{Explanation}:
\\ 
Reads 01 from right to left. Therefore it is not a palindrome.
\end{flushleft}

\paragraph{Follow up:}

\begin{itemize}
\item Coud you solve it without converting the integer to a string?
\end{itemize}

\subsection{Revert half of the number}
\begin{itemize}
\item 为了避免在转换过程中整数产生overflow，因此可以revert only last half of $x$。然后比较这个反转后的部分和first half $x$是否相等。
\item 所有的负数都不是palindrome number
\item 所有10的倍数也都不是palindrome number
\item 得到last half of $x$的方法是将$x$不断除以10，而反转的那部分number是不断乘以10，因此如果发现某个时候$x$小于或者反转的部分，就表明已经处理完了一半的$x$了。
\item 不过，当$x$的长度是奇数时，例如\textbf{12321}，当处理完一半$x$时，反转的number是123，而$x$变成了12。这时候还需要检查$x$是否等于$123/10$。
\end{itemize}
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{Check if the integer is a palindrome number}
\begin{algorithmic}[1]
\Procedure{IsPalindrome}{$x$}
\If{$x < 0$ \textbf{or} $x \bmod 10 \equiv 0$} \Comment 负数和10的倍数都不是palindrome number
\State \Return \texttt{false} 
\EndIf
\State \textbf{$y := 0$} \Comment $y$ 是reversed last half of $x$
\While{$x > y$} 
\State $q := N\div 10$
\State $r := N\bmod 10$
\State $y \gets y\times 10 + r$
\State $x\gets y$ 
\EndWhile
\If{$x \neq y$ \textbf{and} $x \neq y/10$} 
\State \Return \texttt{false}
\Else
\State \Return \texttt{true}
\EndIf
\EndProcedure
\end{algorithmic}
\end{algorithm}
\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Revert half of the number}]
bool isPalindrome( int x )
{
    //negative number or mulitiple of 10
    //are not palindrom number
    if( x < 0 )
    {
        return false;
    }

    if( ( x >= 10 ) && ( x % 10 ) == 0 )
    {
        return false;
    }

    int y = 0;

    while( x > y )
    {
        int q = x / 10;
        int r = x -  q * 10;

        y = y * 10 + r;

        x = q;
    }

    //either x=y or x*10=y
    if( ( x == y ) || ( y / 10 == x ) )
    {
        return true;
    }

    return false;
}
\end{lstlisting}