\section{37 --- Sudoku Solver}
Write a program to solve a Sudoku puzzle by filling the empty cells.

A sudoku solution must satisfy all of the following rules:

\begin{itemize}
\item Each of the digits $1--9$ must occur exactly once in each row.
\item Each of the digits $1--9$ must occur exactly once in each column.
\item Each of the the digits 1-9 must occur exactly once in each of the 9 $3\times 3$ sub-boxes of the grid.
\item Empty cells are indicated by the character dot.
\end{itemize}

\subsection{Depth First Fill}

\begin{itemize}
\item 从$[0,0]$开始填充，
\item 对于每个需要填入数字的空格，从1到9逐个进行测试，看是否在其所在行，列以及所处的九宫格里没有重复数字，如果没有就继续下一次递归（下面的算法中首先进行列的填充）。如果无法成功，则需要把把数字重新设为dot做backtracking。
\item 判断新加入的数字是否合法时，只需要判定当前数字是否合法，不需要判定这个数组是否为数独数组，因为之前加进的数字都是合法的。
\item 对于block的判断：假设当前在 cell $[r,c]$，那么这个格子所在的九宫格的左上角起始位置坐标为$[\lfloor r/3\rfloor\times 3, \lfloor c/3\rfloor\times 3]$
\end{itemize}
\subsubsection{Algorithm}
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{Solve Sudoku}
\begin{algorithmic}[1]
\Procedure{SolveSudoku}{$B$}
\State \Call{Solve}{$B, 0,0$}
\EndProcedure
\end{algorithmic}
\end{algorithm}

Function \texttt{Solve} recursively solves the sudoko by backtracking. This function try to fill each column first and then each row.
\begin{algorithm}[H]
\caption{Backtracking}
\begin{algorithmic}[1]
\Function{Solve}{$B, r, c$}
\If{$r = 9$}
\State \Return \texttt{True} \Comment Completely fill all blanks
\EndIf
\If{$c = 9$}
\State \Call{Solve}{$B, r+1, 0$} \Comment Completely fill column $c$, go to next row $r+1$.
\EndIf
\If{$B[r][c]$ is not filled} \Comment This is a blank field
\For{$i:=1$ \textbf{to} 9} \label{037DFSLoop1}
\State $B[r][c] \gets i$ \Comment fill number $i$
\State $b:=$\Call{IsValid}{$B, r, c$} \Comment Check if the filled cell can make board valid
\If{$b$ is \texttt{true}}
\State $\hat{b}\gets$\Call{Solve}{$B, r, c+1$} \Comment Recursively going to next column
\If{$\hat{b}$ is \texttt{true}} 
\State \Return \texttt{true} \Comment Successfully solved the sudoko
\EndIf
\EndIf
\State Reset $B[r][c]$ to blank \Comment Backtracking
\EndFor \Comment End \ref{037DFSLoop1}
\Else
\State $\hat{b}\gets$\Call{Solve}{$B, r, c+1$} \Comment This cell is already filled, go to next column
\State \Return $\hat{b}$
\EndIf
\EndFunction
\end{algorithmic}
\end{algorithm}

Function \texttt{IsValid} checks if the input board is valid sudoko 
\begin{algorithm}[H]
\caption{Check If The Board Is Valid}
\begin{algorithmic}[1]
\Function{IsValid}{$B, r, c$}
\For{$i:=0$ \textbf{to} 8}
\If{$i\neq c$ \textbf{and} $B[r][c] = B[r][i]$}
\State \Return \texttt{false} \Comment Found duplicate number in column $i$
\EndIf
\If{$i\neq r$ \textbf{and} $B[r][c] = B[i][c]$}
\State \Return \texttt{false} \Comment Found duplicate number in row $i$
\EndIf
\State $x:=\lfloor r/3\rfloor \times 3 + \lfloor i/3\rfloor$ \Comment The row index of $i$th element in current block
\State $y:=\lfloor c/3\rfloor \times 3 + i\bmod 3$ \Comment The column index of $i$th element in current block
\If{$x\neq r$ \textbf{or} $y \neq c$}
\If{$B[r][c] = B[x][y]$}
\State \Return \texttt{false} \Comment Found duplicate number in $i$th element of current block
\EndIf
\EndIf
\EndFor
\State \Return \textbf{true} \Comment The board is valid
\EndFunction
\end{algorithmic}
\end{algorithm}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Backtrack}]
void solveSudoku( vector<vector<char>>& board )
{
    solve( board, 0, 0 );
}

bool solve( vector<vector<char>>& B, int r, int c )
{
    if( r == 9 )
    {
        return true;
    }

    if( c == 9 )
    {
        return solve( B, r + 1, 0 );
    }

    if( B[r][c] != '.' )
    {
        //this cell is filled
        //try next column
        return solve( B, r, c + 1 );
    }

    for( char d = '1'; d <= '9'; ++d )
    {
        B[r][c] = d;

        if( is_valid( B, r, c ) )
        {
            if( solve( B, r, c + 1 ) )
            {
                return true;
            }
        }
    }

    //no success
    //reset to blank to backtrack
    B[r][c] = '.';
    return false;
}

bool is_valid( vector<vector<char>>& B, int r, int c )
{
    auto d = B[r][c];
    for( int i = 0; i < 9; ++i )
    {
        if( ( i != r ) && ( B[i][c] == d ) )
        {
            //duplate cell in row i
            return false;
        }

        if( ( c != i ) && ( B[r][i] == d ) )
        {
            //duplicate cell in column i
            return false;
        }

        //the row and column
        //of i-th element in current block
        int br = r / 3 * 3 + i / 3;
        int bc = c / 3 * 3 + i % 3;

        if( ( br != r ) || ( bc != c ) )
        {
            if( B[br][bc] == d )
            {
                //duplicate at i-th element
                //of current block
                return false;
            }
        }
    }

    return true;
}
\end{lstlisting}