\section{45 --- Jump Game II}
Given an array of non-negative integers $A$, you are initially positioned at the first index of the array.

Each element in the array represents your maximum jump length at that position.

Your goal is to reach the last index in the minimum number of jumps.

\paragraph{Example:}

\begin{flushleft}
\textbf{Input}: $[2,3,1,1,4]$

\textbf{Output}: 2

\textbf{Explanation}: 

The minimum number of jumps to reach the last index is 2. 

Jump 1 step from index 0 to 1, then 3 steps to the last index.
\end{flushleft}


\paragraph{Note:}

\begin{itemize}
\item You can assume that you can always reach the last index.
\end{itemize}


\subsection{BFS}
可以把每次所能到达的位置按照所需的jump数排成一个树状结构。例如，按照给定的例子，可以有如下的graph

%\begin{tikzpicture}[modal][H]
%\node[world] (2) [label=left:{level 0:}]{$2$};
%\node[world] (3) [label=left:{level 1:}, below = 2mm of 2]{$3$};
%\node[world] (1) [right = 2mm of 3]{$1$};
%\node[world] (11) [label=left:{level 2:}, below = 2mm of 3]{$1$};
%\node[world] (4) [right = 2mm of 11]{$4$};    
%\end{tikzpicture}
\begin{itemize}
\item 第0层就是位置为0的节点，它所能跳到的位置为1和2，也就是第1层的两个节点。
\item 第1层有位置为1和2的两个节点，其中位置1的节点，它能跳到位置2，3，4，而位置2已经在第1层了，所以第2层有位置3和4，位置2的节点，它能跳到位置3，所以第2层有位置3
\item 综合第1层的分析，第2层就有位置3和4的节点，而位置4已经是最后一个位置了，所以跳到4至少需要2步。
\end{itemize}

算法实现中，需要维护当前level所能跳到的最大位置，以及下一个level所能跳到的最大位置，然后遍历当前level，更新下一个level的最大位置，如果已经到达最后一个位置，就直接返回层数。

\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{BFS}
\begin{algorithmic}[1]
\Procedure{Jump}{$A, n$}
\If{$n = 1$}
\State \Return 0 \Comment We already in the final position
\EndIf
\State $e_0 := 0$ \Comment The maximum position of current level
\State $e_1 := 0$ \Comment The maximum position of next level
\State $P:=0$ \Comment The current position
\State $\ell := 1$ \Comment We already in the zero level, next level will be level 1
\State $\ast$ Update next level's positions that can be reached
\While{$P \leq e_0$}
\State $e_1 \gets \max(e_1, A[P]+P)$ \Comment Update the maximum position of next level
\If{$e_1 \geq n-1$} \Comment Next level will contain the final position
\State \Return $\ell$
\EndIf
\If{$P = e_0$} \Comment Already in the end of current level
\State $e_0 \gets e_1$ \Comment Update as the maximum position of next level
\State $\ell\gets \ell+1$ \Comment Increments the number of levels
\EndIf
\State $P \gets P+1$ \Comment Move to next position
\EndWhile
\State \Return $\infty$ \Comment Cannot jump to the final position
\EndProcedure
\end{algorithmic}
\end{algorithm}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={BFS}]
int jump( vector<int>& nums )
{
    if( nums.size() == 1 )
    {
        return 0;
    }

    int L = static_cast<int>( nums.size() );

    int pos = 0;

    int cur_end = 0;
    int next_end = 0;

    //since current end is not the final end
    //we at least requires 1 jump
    int jumps = 1;

    while( pos <= cur_end )
    {
        next_end = ( max )( pos + nums[pos], next_end );

        if( next_end >= L - 1 )
        {
            //can jump to the final position
            return jumps;
        }

        if( pos == cur_end )
        {
            //move to next level
            cur_end = next_end;
            //increment the number of jumps
            ++jumps;
        }

        //test next position
        pos = pos + 1;
    }

    //cannot jump to final position
    return -1;
}
\end{lstlisting}