\section{75 --- Sort Colors}
Given an array with $n$ objects colored red, white or blue, sort them \textbf{in-place} so that objects of the same color are adjacent, with the colors in the order red, white and blue.

Here, we will use the integers 0, 1, and 2 to represent the color red, white, and blue respectively.

Note: You are not suppose to use the library's sort function for this problem.

\paragraph{Example:}
\begin{flushleft}

\textbf{Input}: \fcj{[2,0,2,1,1,0]}

\textbf{Output}: \fcj{[0,0,1,1,2,2]}
\end{flushleft}

\paragraph{Follow up:}

\begin{itemize}
\item Could you come up with a one-pass algorithm using only constant space?
\end{itemize}

\subsection{Dutch National Flag Problem}
The problem is known as \textbf{Dutch National Flag Problem} and first was proposed by \textbf{Edsger W. Dijkstra}. The idea is to attribute a color to each number and then to arrange them following the order of colors on the Dutch flag.

The approach makes use of three pointers (indexes) to track the rightmost boundary of zeros ($p_0$), the leftmost boundary of twos ($p_2$) and the current element under the consideration ($p_1$).

The idea is to move $p_1$ along the array, if $A[p_1] = 0$, swap it with $A[p_0]$, and if $A[p_1] = 2$, swap it with $A[p_2]$.

\begin{enumerate}
\item Initialize the rightmost boundary of \textbf{zeros}: $p_0 = 0$. During the algorithm execution, $A[i < p_0] = 0$.

\item Initialize the leftmost boundary of \textbf{twos}: $p_2 = n - 1$. During the algorithm execution, $A[i > p_2] = 2$.

\item Initialise the index of current element to consider: $p_1 = 0$.

\item The iteration will stop when $p_1 > p_2$. During the iterating $A$

\begin{itemize}
\item If $A[p_1] = 0$: swap $A[p_1]$ and $A[p_0]$ and move both pointers to the right.
\item If $A[p_1] = 2$: swap $A[p_1]$ and $A[p_2]$ and move $p_2$ to the left.
\item If $A[p_1] = 1$: move $p_1$ to the right.
\end{itemize}
\end{enumerate}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={One Pass}]
void sortColors( vector<int>& nums )
{
    int n = static_cast<int>( nums.size() );
    int p0 = 0;
    int p1 = 0;
    int p2 = n - 1;
    while( p1 <= p2 )
    {
        if( nums[p1] == 0 )
        {
            swap( nums[p1], nums[p0] );
            //move both p0 and p1 right
            ++p0;
            ++p1;
        }
        else if( nums[p1] == 2 )
        {
            swap( nums[p1], nums[p2] );
            //only move left p2
            --p2;
        }
        else
        {
            //only move p1 right
            ++p1;
        }
    }
}
\end{lstlisting}
