\section{81 -- Search in Rotated Sorted Array II}
Suppose an array $A$ sorted in ascending order is rotated at some pivot unknown to you beforehand. (i.e., $(0,0,1,2,2,5,6)$ might become $(2,5,6,0,0,1,2)$).
\par
You are given a target value $T$ to search. If found in the array return 1, otherwise return 0.
\paragraph{Example 1:}
\begin{flushleft}
\textbf{Input}: $A = [2,5,6,0,0,1,2]$, $T = 0$
\\
\textbf{Output}: 1
\end{flushleft}
\paragraph{Example 2:}
\begin{flushleft}
\textbf{Input}: $A = [2,5,6,0,0,1,2]$, $T = 3$
\\
\textbf{Output}: 0
\end{flushleft}
\paragraph{Follow up:}
\begin{itemize}
    \item This is a follow up problem to Search in Rotated Sorted Array, where $A$ may contain duplicates. Would this affect the run-time complexity? How and why?
\end{itemize}
\subsection{Binary Search And Linear Search}
\begin{CJK*}{UTF8}{gbsn}
主要的难点难点在于我们不知道原数组在哪旋转了，不过可以通过观察例子找出规律。 例如$A=(0, 1, 2, 4, 5, 6, 7)$ 共有下列七种旋转方法：

\begin{table}[H]
\begin{tabular}{lllllll}
0 & 1 & 2 & {\color{red} 4} & 5 & 6 & 7 \\
7 & 0 & 1 & {\color{red} 2} & 4 & 5 & 6 \\
6 & 7 & 0 & {\color{red} 1} & 2 & 4 & 5 \\
5 & 6 & 7 & {\color{red} 0} & 1 & 2 & 4 \\
4 & 5 & 6 & {\color{red} 7} & 0 & 1 & 2 \\
2 & 4 & 5 & {\color{red} 6} & 7 & 0 & 1 \\
1 & 2 & 4 & {\color{red} 5} & 6 & 7 & 0
\end{tabular}
\end{table}
可以看到如果中间的数小于最右边的数，最小值在左半段，若中间数大于最右边数，则最小值就出现在右半段。因此首先用二分法寻找从左至右第一个最小值出现的位置。如果中间的数小于最右边的数，则在左半段寻找，这是右边界设为中间位置，若中间数大于最右边数，则在右半段寻找，这是左边界设置为中间位置加1。而如果可以有重复值，就会出现来面两种情况，$(3, 1, 1)$ 和 $(1,1,3,1)$，对于这两种情况中间值等于最右值时，目标值3既可以在左边又可以在右边，对于这种情况就要把右边界向左移动一位，如果还相同则继续移，直到移到不同值为止。
\par
但是这种方法找到的最小值是从左到右的第一个，但不是旋转发生的位置。例如$(1,1,1,3,1)$，从左到右的第一个最小值位置是0， 但是发生旋转的位置发生在4。这时候，我们需要从当前找到的位置向左移动，如果小于0，就从数组末尾开始左移，直到找到第一个不同于这个最小值的位置。这个位置往前加1就是旋转发生的地址。
\par
找到旋转发生的index，我们就知道了原数组每个元素在旋转后的数组中的位置。假设某个元素在原数组中的位置为$i$，旋转发生的位置为$t$，那么其在旋转后的数组中的位置就是$(i+t)\bmod L$。$L$是数组的长度。于是接着用leftmost binary search寻找是否存在目标值。
\end{CJK*}
\subsubsection{Code}
Procedure \texttt{Search} search a target $T$ in a rotated sorted array $A$ with length $L$.
\setcounter{algorithm}{0}
\begin{algorithm}[H]
\caption{Binary Search With Linear Search}
\begin{algorithmic}[1]
\Procedure{Search}{$A, L, T$}
\State $l:=0, r:=L-1$ \Comment The binary seach left and right index
\While{$l < r$}
\State $m:=(l+r)/2$
\If{$A[m] > A[r]$} \Comment The minimum value is in right hand
\State $l\gets m+1$
\ElsIf{$A[m] < A[r]$}
\State $r \gets m$ \Comment The minimum value is in left hand
\Else \Comment The middle value is same as the right value
\State $r\gets r-1$ \Comment Decrements right index
\EndIf
\EndWhile
\State $\alpha:= (l - 1 + L) \bmod L$ \Comment The index that rotation happens
\While{$\alpha \neq l$}
\If{$A[\alpha] \neq A[l]$}
\State \texttt{break} \Comment Found the rotate position.
\Else
\State $\alpha \gets (\alpha-1+L)\bmod L$ \Comment Keep left shit
\algstore{81algo}
\end{algorithmic}
\end{algorithm}
\begin{algorithm}[H]
\begin{algorithmic}[1]
\algrestore{81algo}
\EndIf
\EndWhile
\If{$\alpha = l$} \Comment All elements in $A$ are equal
\If{$A[\alpha]=T$}
\State \Return 1
\Else
\State \Return 0;
\EndIf
\EndIf
\State $l\gets 0,\; r\gets L$ \Comment Prepare for leftmost binary search
\While{$l< r$}
\State $m:=(l+r)/2$
\State $\hat{m}:=(m+\alpha)\bmod L$ \Comment The middle index in current rotated array
\If{$A[\hat{m}] < T$} \Comment Search in right side of non-rotated array
\State $l\gets m+1$
\Else
\State $r \gets m$ \Comment Search in left side of non-rotated array
\EndIf
\EndWhile
\State $\hat{l}:=(l+\alpha)\bmod L$ \Comment $\hat{l}$ is the found index in current rotated array
\If{$A[\hat{l}] = T$} \Comment $A[l]$ is the first element in non-rotated array no less than $T$
\State \Return 1
\Else
\State \Return 0
\EndIf
\EndProcedure
\end{algorithmic}
\end{algorithm}