\section{409 --- Longest Palindrome}
Given a string $S$ which consists of lowercase or uppercase letters, find the length of the longest palindromes that can be built with those letters.
\par
This is case sensitive, for example \texttt{Aa} is not considered a palindrome here.

\paragraph{Note:}
\begin{itemize}
\item Assume the length of given string will not exceed 1,010.
\end{itemize}

\paragraph{Example:}

\begin{flushleft}
\textbf{Input}: \texttt{abccccdd}
\\
\textbf{Output}: 7
\\
\textbf{Explanation}: One longest palindrome that can be built is \texttt{dccaccd}, whose length is 7.
\end{flushleft}

\subsection{Counting}
\begin{itemize}
\item We can only incorporate only one character with largest odd counts into the palindrome even if multiple characters may have same largest odd counts.
\item For any other character with odd counts $x$ , we can incorporate this one with $x-1$ times into the palindrome.
\item The fast way to do this is just add $x-1$ into the result when iterating over the counts array. Also, record the maximum odd counts $y$. At the end, we subtract $(y-1)$ from the result and add back $y$. This is effectively equal to add 1 to the result.
\item Of course, If all characters are have even counts, there is no need to add 1 to the result.
\end{itemize}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Counting}]
int longestPalindrome( string s )
{
    //lower case
    int l[26] = {0};
    //uppercase
    int u[26] = {0};

    for( auto c : s )
    {
        if( ( c >= 'a' ) && ( c <= 'z' ) )
        {
            l[c - 'a'] += 1;
        }
        else
        {
            u[c - 'A'] += 1;
        }
    }

    int ans = 0;
    int max_odd_len = 0;
    for( int i = 0; i < 26; ++i )
    {
        if( l[i] & 1 )
        {
            //character i+'a' can be added at least l[i]-1 times
            max_odd_len = ( max )( max_odd_len, l[i] );
            ans += ( l[i] - 1 );
        }
        else
        {
            ans += l[i];
        }

        if( u[i] & 1 )
        {
            //character i+'A' can be added at least u[i]-1 times
            max_odd_len = ( max )( max_odd_len, u[i] );
            ans += ( u[i] - 1 );
        }
        else
        {
            ans += u[i];
        }
    }

    //ans-(max_odd_len-1)+max_odd_len = ans + 1
    //only happens when there exits odd counts characters
    return max_odd_len == 0 ? ans : ans + 1;
}
\end{lstlisting}
