\section{419 --- Battleships in a Board}
Given an 2D board, count how many battleships are in it. The battleships are represented with \texttt{X}s, empty slots are represented with dots. You may assume the following rules:

\begin{itemize}
\item You receive a valid board, made of only battleships or empty slots.
\item Battleships can only be placed horizontally or vertically. In other words, they can only be made of the shape $1\times N$ (1 row, $N$ columns) or $N\times 1$ (N rows, 1 column), where $N$ can be of any size.
\item At least one horizontal or vertical cell separates between two battleships - there are no adjacent battleships.
\end{itemize}

\paragraph{Example}:
\begin{flushleft}
\begin{table}[H]
\begin{tabular}{cccc}
\texttt{X} & . & . & \texttt{X}\\
. & . & . & \texttt{X}\\
. & . & . & \texttt{X}
\end{tabular}
\end{table}
In the above board there are 2 battleships.
\end{flushleft}

\paragraph{Invalid Example:}

\begin{flushleft}
\begin{table}[H]
\begin{tabular}{cccc}
. & . & . & \texttt{X}\\
\texttt{X} & \texttt{X} & \texttt{X} & \texttt{X}\\
. & . & . & \texttt{X}
\end{tabular}
\end{table}
This is an invalid board that you will not receive - as battleships will always have a cell separating between them.
\end{flushleft}


\paragraph{Follow up:}
\begin{itemize}
\item Could you do it in one-pass, using only $O(1)$ extra memory and without modifying the value of the board?
\end{itemize}

\subsection{Find the start of the battleship}
Iterating over all cells, we can count only those that are the \texttt{first} cell of the battleship. \textbf{First cell} will be defined as the most \textbf{top-left} \texttt{X} cell. We can check for first cells by only counting the \texttt{X} cells that do not have an \texttt{X} to the left and do not have an \texttt{X} above them.

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Top-left cell}]
int countBattleships( vector<vector<char>>& board )
{
    int m = static_cast<int>( board.size() );
    int n = static_cast<int>( board[0].size() );

    int ans = 0;

    for( int r = 0; r < m; ++r )
    {
        for( int c = 0; c < n; ++c )
        {
            if( board[r][c] == 'X' )
            {
                unsigned char valid = 0;
                //Either the left is dot or this cell is the start cell of current row
                if( ( ( r > 0 ) && ( board[r - 1][c] == '.' ) ) || ( r == 0 ) )
                {
                    valid += 1;
                }

                //Either the top is dot or this cell is the start cell of current column
                if( ( ( c > 0 ) && ( board[r][c - 1] == '.' ) ) || ( c == 0 ) )
                {
                    valid += 2;
                }

                //only in these two cases, this cell is the start of a battleship
                if( valid == 3 || valid == 0 )
                {
                    ++ans;
                }
            }
        }
    }

    return ans;
}
\end{lstlisting}
