\section{424 --- Longest Repeating Character Replacement}
Given a string $s$ that consists of only uppercase English letters, you can replace any letter in the string with another letter at most $ k $ times. Find the length of a longest substring containing all repeating letters you can get after performing the above operations.

\paragraph{Note:}
\begin{itemize}
\item Both the string's length and k will not exceed $10^4$.
\end{itemize}

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: $s = \texttt{ABAB}$, $k = 2$

\textbf{Output}: 4

\textbf{Explanation}: 

Replace the two \texttt{A}s with two \texttt{B}s or vice versa.
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: $s = \texttt{AABABBA}$, $k = 1$

\textbf{Output}: 4

\textbf{Explanation}:

Replace the one \texttt{A} in the middle with \texttt{B} and form \texttt{AABBBBA}.

The substring \texttt{BBBB} has the longest repeating letters, which is 4.
\end{flushleft}

\subsection{Sliding Window}
\begin{itemize}
\item 与所有使用sliding window算法类似，同样需要左右两个index $l$和$r$。
\item 统计窗口$A[l,r]$中出现次数最多的letter $c$的个数，记为$\delta$。
\item 当窗口的length $\ell$与$\delta$的difference等于$k+1$时，表明可以将窗口中其他的 $k$个letter替换为$c$，这时候，这时候$A[l+1, r]$之间的所有其他字符都可以替换为同一个字符。注意这个时候这个字符可能不是$c$。
\begin{enumerate}
\item 如果$A[l]=c$，如果这时候$A[l+1,r]$之间的出现最多的letter不是$c$，而是另外一个letter，假设是$c_1$，那么$c_1$的出现次数必然为$\delta$。那么把$A[l+1,r]$中的其他字符替换为$c_1$即得到$r-(l+1)+1$长度的重复字符。
\item 反之，如果$A[l]\neq c$，那么$A[l+1,c]$中$c$仍然是出现最多的letter，那么把$A[l+1,r]$中的其他字符替换为$c$也是得到$r-(l+1)+1$长度的重复字符。
\end{enumerate}
由此可见，两种情况下，所能得到的最长的重复字符长度都是$r-(l+1)+1$。
\end{itemize}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Sliding Window}]
int characterReplacement( string s, int k )
{
    int L = static_cast<int>( s.size() );

    int l = 0;
    int r = 0;

    int m[26] = {0};

    int max_cnt = 0;

    int best = 0;

    while( r < L )
    {
        m[s[r] - 'A'] += 1;
        max_cnt = ( max )( max_cnt, m[s[r] - 'A'] );

        if( r - l + 1 - max_cnt == k + 1 )
        {
            //increments the left boundary
            m[s[l] - 'A'] -= 1;
            ++l;
        }

        //A[l,r] can have all same letters
        best = ( max )( best, r - l + 1 );

        ++r;
    }

    return best;
}
\end{lstlisting}