\section{443 --- String Compression}
Given an array of characters $A$, compress it in-place.

The length after compression must always be smaller than or equal to the original array.

Every element of the array should be a character (not int) of length 1.

After you are done modifying the input array in-place, return the new length of the array.

 
\paragraph{Follow up:}

\begin{itemize}
\item Could you solve it using only $\mathrm{O}(1)$ extra space?
\end{itemize}

 
\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: $[a,a,b,b,c,c,c]$

\textbf{Output}: Return 6, and the first 6 characters of the input array should be: $[a,2,b,2,c,3]$

\textbf{Explanation}: $aa$ is replaced by $a2$. $bb$ is replaced by $b2$. $ccc$ is replaced by $c3$.
 
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: $[a]$

\textbf{Output}: Return 1, and the first 1 characters of the input array should be: $[a]$

\textbf{Explanation}: Nothing is replaced.

\end{flushleft}


\paragraph{Example 3:}

\begin{flushleft}
\textbf{Input}: $[a,b,b,b,b,b,b,b,b,b,b,b,b]$

\textbf{Output}: Return 4, and the first 4 characters of the input array should be: $[a,b,1,2]$.

\textbf{Explanation}: Since the character a does not repeat, it is not compressed. $bbbbbbbbbbbb$ is replaced by $b12$. Notice each digit has it's own entry in the array.
 

\end{flushleft}


\paragraph{Note:}

\begin{itemize}
\item All characters have an ASCII value in $[35, 126]$.
\item $1 \leq \lvert A\rvert \leq 1000$.
\end{itemize}

\subsection{Two Pointers}
\begin{itemize}
\item Maintain three pointers $w$, $r$ and $a$
\item $w$ is the position where we just write
\item $r$ is the position we are current at
\item $a$ is the first position of a sequence of duplicate letters
\item whenever we found different letters in two adjacent indices, this is the change of state. Write the count of duplicate letters and update $w$. And then update $a$ as the index of the new letter.
\end{itemize}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Read And Write Pointers}]
int compress( vector<char>& chars )
{
    int w = 0; //write
    int a = 0; //anchor

    int L = static_cast<int>( chars.size() );

    for( int r = 0; r < L; ++r )
    {
        if( ( r + 1 == L ) || ( chars[r] != chars[r + 1] ) )
        {
            //state of change
            int count = r - a + 1;

            chars[w] = chars[a];
            ++w;

            if( count > 1 )
            {
                //write count when count
                //is larger than 1
                auto s = to_string( count );
                for( auto c : s )
                {
                    chars[w] = c;
                    ++w;
                }
            }

            //update anchor position
            a = r + 1;
        }
    }

    return w;
}
\end{lstlisting}