\section{455 --- Assign Cookies}
Assume you are an awesome parent and want to give your children some cookies. But, you should give each child at most one cookie. Each child $i$ has a greed factor $g_i$, which is the minimum size of a cookie that the child will be content with; and each cookie $j$ has a size $s_j$. If $s_j \geq g_i$, we can assign the cookie $j$ to the child $i$, and the child $i$ will be content. Your goal is to maximize the number of your content children and output the maximum number.

\paragraph{Note:}
\begin{itemize}
\item You may assume the greed factor is always positive.
\item You cannot assign more than one cookie to one child.
\end{itemize}


\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: $g=[1,2,3]$, $s=[1,1]$

\textbf{Output}: 1

\textbf{Explanation}: 

You have 3 children and 2 cookies. The greed factors of 3 children are 1, 2, 3. And even though you have 2 cookies, since their size is both 1, you could only make the child whose greed factor is 1 content.

You need to output 1.
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: $g=[1,2]$, $s=[1,2,3]$

\textbf{Output}: 2

\textbf{Explanation}: 

You have 2 children and 3 cookies. The greed factors of 2 children are 1, 2. You have 3 cookies and their sizes are big enough to gratify all of the children, You need to output 2.
\end{flushleft}

\subsection{Sorting And Binary Search}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Binary Search}]
int findContentChildren( vector<int>& g, vector<int>& s )
{

    //we need binary search
    //sort both first
    sort( g.begin(), g.end() );

    sort( s.begin(), s.end() );

    int ans = 0;

    //the search start in g
    int last = 0;

    //we need to find which cookie can satisfy
    for( int x : g )
    {
        int l = last;
        int r = static_cast<int>( s.size() );

        if( l == r )
        {
            break;
        }

        //leftmost binary search
        while( l < r )
        {
            int mid = ( l + r ) / 2;

            if( s[mid] < x )
            {
                l = mid + 1;
            }
            else
            {
                r = mid;
            }
        }

        if( l < static_cast<int>( s.size() ) )
        {
            //this cookie can be
            //consumed by current child with greed x
            ++ans;
        }
        else
        {
            //otherwise, since greedy is sorted,
            //no cookie can satisfy any more child
            break;
        }


        //since the cookie is consumed
        //set the start of search to the next one
        last = l + 1;

    }

    return ans;
}
\end{lstlisting}
