\section{456 --- 132 Pattern}
Given a sequence of $n$ integers $a_1$, $a_2$, $\ldots$, $a_n$, a 132 pattern is a subsequence $a_i$, $a_j$, $a_k$ such that $i < j < k$ and $a_i < a_k < a_j$. Design an algorithm that takes a list of $n $ numbers as input and checks whether there is a 132 pattern in the list.

Note: $n$ will be less than 15,000.

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: [1, 2, 3, 4]

\textbf{Output}: \texttt{False}

\textbf{Explanation}: There is no 132 pattern in the sequence.
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: [3, 1, 4, 2]

\textbf{Output}: \texttt{True}

\textbf{Explanation}: There is a 132 pattern in the sequence: $[1, 4, 2]$.
\end{flushleft}

\paragraph{Example 3:}

\begin{flushleft}
\textbf{Input}: [-1, 3, 2, 0]

\textbf{Output}: \texttt{True}

\textbf{Explanation}: There are three 132 patterns in the sequence: [-1, 3, 2], [-1, 3, 0] and [-1, 2, 0].

\end{flushleft}

\subsection{Brute Froce}
The most direct approach is to test each $(i,j,k)$ to check if the corresponding numbers satisfy the 132 criteria.

To improve the efficiency, we can observe the following fact: For a number $A[j]$, if we find a smallest $A[i]$ such that $A[i] < A[j]$ and $i<j$, then for any $k> j$, the likelihood that $A[k]$ is between $A[i]$ and $A[j]$ is increased.

Thus, we can keep track of minimum number $x$ until $j$, and then check all the index $k> j$ to see if there is any $A[k]<A[j]$ and $A[k]> x$.

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Better Brute Force}]
bool find132pattern( vector<int>& nums )
{
    if( nums.empty() || nums.size() < 3 )
    {
        return false;
    }

    int x = nums[0];

    for( size_t j = 0; j < nums.size() - 1; ++j )
    {
        //keep track of minimum number so far
        x = ( min )( x, nums[j] );

        for( size_t k = j + 1; k < nums.size(); ++k )
        {
            //nums[k] is in [x, nums[j]]
            if( ( nums[k] < nums[j] ) && ( nums[k] > x ) )
            {
                return true;
            }
        }
    }

    return false;
}
\end{lstlisting}

\subsection{Searching Intervals}
This approach is relying on the fact: to maximize the likelihood that we can find $A[k]$, $A[i]$ and $A[j]$ must be the start and end points of a local increasing segment. 

To achieve this, we can keep track of minimum number, $x$, found after the last peak.  Whenever we encounter $A[y] < A[y-1]$, we know that $A[y-1]$ was the endpoint of the last found increasing segment. Thus, we can iterate over $k > y$ to find the 132 pattern.

But, we can bypass the iteration process if we can store all the local increasing segments found so far. Therefore, during the traversing, suppose $x$ is the start of a segment, whenever we find $A[y] < A[y-1]$, add the local increasing segment $A[x\ldots y-1]$ into the stored ranges. At the same time, we check if the current number falls in any of the ranges found so far. If so, 132 pattern is found.

If no such element is found at the end, this means we cannot find 132 pattern in $A$.

\begin{lstlisting}[style=customc, caption={Search Intervals}]
bool find132pattern( vector<int>& nums )
{

    size_t x = 0;

    //store the local increasing segments so far
    vector<array<int, 2>> segs;

    for( size_t y = 1; y < nums.size(); ++y )
    {
        if( nums[y - 1] > nums[y] ) //or nums[y - 1] >= nums[y]
        {
            //the last local increasing segment
            //ends
            if( x < y - 1 )
            {
                //exclude the case x=y-1
                //add local increasing segment
                //[x,y-1] to the stored segs
                segs.push_back( array<int, 2> {x, y - 1} );
            }

            //update next segement start as y
            x = y;
        }

        //check if nums[y] is in the ranges that in segs
        for( const auto& seg : segs )
        {
            if( ( nums[seg[0]] < nums[y] ) && ( nums[y] < nums[seg[1]] ) )
            {
                return true;
            }
        }
    }

    return false;
}
\end{lstlisting}

 

\subsection{Stack With Minimum Number Array}
Based on the last approach, we can make the process of finding $A[k]$ faster if we store the minimum value in $A[0,j-1]$ when considering $A[j]$ in an array, say $B[j]$. 

After $B$ is created, we need to maintain a list of $A[k]$ ($k>j$), such that they are larger than $B[j]$. From these $A[k]$ candidates, the best one is the minimum of them, say $A[\hat{k}]$. If $A[\hat{k}] < A[j]$, 132 pattern is found. 

The best way to keep track of these $A[k]$ is using a stack and traverse from the end of $A$. We place the minimum of $A[k]$ candidates on the top of the stack. 

\begin{itemize}
\item if $A[j] \leq B[j]$, continue to $A[j-1]$
\item Otherwise, we keep on popping from the stack until the top element is larger than $B[j]$. This process ensures that 
\begin{enumerate}
\item All remaining elements in the stack are larger than $B[j]$.
\item All popped elements from the stack are $\leq B[j]$. In array $B$, if $u > v$, we have $B[u]\leq B[v]$. Therefore, for any index $t$ less than $j$, $B[j]\leq B[t]$, and then all these popped elements are also $\leq B[t]$. This means these popped elements cannot be the candidates even for any $A[t]$ where $0\leq t <j$. 
\end{enumerate}
\item  If current top element of the stack is less than $A[j]$, 132 pattern is found. Otherwise, we push $A[j]$ into the stack. The reason is: $A[j] \geq B[j]$, so $A[j]$ could be a candidate to satisfy a 132 pattern for the elements before $B[j]$. We can note that, pushing $A[j]$ into the stack still making sure the contained elements are sorted.
\item One more thing to note is that when $A[j]\leq B[j]$, we don't push $A[j]$ into the stack because $A[j]$ is less than the minimum of elements of its left and cannot be the candidate of $A[k]$.
\end{itemize}

\begin{lstlisting}[style=customc, caption={Stack With Minimum Number Array}]
bool find132pattern( vector<int>& nums )
{
    if( nums.empty() )
    {
        return false;
    }

    //stores the minimum number in nums[0, j-1]
    //when considering element nums[j]
    vector<int> v_min( nums.size() );

    v_min[0] = nums[0];

    for( size_t i = 1; i < nums.size(); ++i )
    {
        v_min[i] = ( min )( v_min[i - 1], nums[i] );
    }

    stack<int> stk;

    for( size_t i = nums.size(); i >= 1; --i )
    {
        //since we using size_t
        //i>=0 will cause infinite loop
        auto j = i - 1;

        if( nums[j] > v_min[j] )
        {
            //only when nums[j] > v_min[j]
            //132 pattern can be possile.

            while( !stk.empty() && ( stk.top() <= v_min[j] ) )
            {
                //pop all the nums[k] that are not
                //candidate
                stk.pop();
            }

            if( !stk.empty() && ( nums[j] > stk.top() ) )
            {
                //found 132 pattern
                return true;
            }

            //push nums[j] to the stack
            //since it is a nums[k] candidate
            //for the elements before v_min[j]
            stk.push( nums[j] );
        }

    }

    return false;
}
\end{lstlisting}
 
\subsection{Only Stack}
We can improve the approach based on stack without using a auxiliary array to store the minimum number.

We can make use of a stack only by tracking the minimum number of the $A[k]$ candidates. We still traverse the array from right end.
\begin{enumerate}
\item We maintain the minimum number so far, say $x$. 
\item If the stack is not empty, and current number $A[i]$ is less than $x$, we know that
\begin{itemize}
\item $A[j]$ must be one of elements in the stack.
\item $x$ is $A[k]$.
\end{itemize}
Thus, we are sure 132 pattern is found.
\item Otherwise, we keep popping the top element when it is less than current number $A[i]$. Thus, we put $A[j]$ candidates into the stack.
\item Whenever the stack pop its top element, update the minimum number so far, $x$, by the popped element. Thus, we obtain the minimum of $A[k]$ candidates.
\item Then, push current number into the stack.
\end{enumerate}
\begin{lstlisting}[style=customc, caption={Stack}]
bool find132pattern( vector<int>& nums )
{
    if( nums.empty() || ( nums.size() < 3 ) )
    {
        return false;
    }

    int L = static_cast<int>( nums.size() );

    int x_k = INT_MIN;

    stack<int> stk;

    for( int i = L - 1; i >= 0; --i )
    {
        //stk is not empty means
        //we have x_j > x_k and (j < k)
        //so if x_i < x_k is found
        //we found the pattern
        if( !stk.empty() && ( nums[i] < x_k ) )
        {
            return true;
        }

        //we put x_j in the stack
        //pop all numbers in the stack that is less than nums[i]
        //the last one will be the latest x_k < x_j
        //this is strict less than, so we use
        //stk.top() < nums[i]
        while( !stk.empty() && ( stk.top() < nums[i] ) )
        {
            //update x_k as the top of the stack
            x_k = stk.top();
            stk.pop();
        }

        //now the numbers in the stack
        //are larger than x_k
        stk.push( nums[i] );
    }

    return false;
}
\end{lstlisting}