\section{482 --- License Key Formatting}
You are given a license key represented as a string $S$ which consists only alphanumeric character and dashes. The string is separated into $N+1$ groups by $N$ dashes.

Given a number $K$, we would want to reformat the strings such that each group contains exactly $K$ characters, except for the first group which could be shorter than $K$, but still must contain at least one character. Furthermore, there must be a dash inserted between two groups and all lowercase letters should be converted to uppercase.

Given a non-empty string $S$ and a number $K$, format the string according to the rules described above.

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: $S = \texttt{5F3Z-2e-9-w}$, $K = 4$

\textbf{Output}: \texttt{5F3Z-2E9W}

\textbf{Explanation}: 

The string S has been split into two parts, each part has 4 characters.
Note that the two extra dashes are not needed and can be removed.
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: $S = \texttt{2-5g-3-J}$, $K = 2$

\textbf{Output}: \texttt{2-5G-3J}

\textbf{Explanation}: 

The string S has been split into three parts, each part has 2 characters except the first part as it could be shorter as mentioned above.
\end{flushleft}


\paragraph{Note:}
\begin{itemize}
\item The length of string S will not exceed 12,000, and K is a positive integer.
\item String $S$ consists only of alphanumerical characters (a--z and/or A--Z and/or 0--9) and dashes(-).
\item String $S$ is non-empty.
\end{itemize}

\subsection{Reverse}
从$S$的最后一个位置开始，往前处理，最后将得到的字符串进行反转。

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Reverse}]
string licenseKeyFormatting( string S, int K )
{
    int L = static_cast<int>( S.size() );

    int read = L - 1;
    int count = 0;

    string ans;
    ans.reserve( S.size() );

    //process from end to start
    while( read >= 0 )
    {
        if( count == K )
        {
            ans.push_back( '-' );
            count = 0;
        }

        char c = S[read];
        if( ( c >= 'a' ) && ( c <= 'z' ) )
        {
            ans.push_back( ( c - 'a' ) + 'A' );
            ++count;
        }
        else if( c != '-' )
        {
            ans.push_back( c );
            ++count;
        }

        --read;

    }

    //we may add an additional dash
    if( ans.back() == '-' )
    {
        ans.pop_back();
    }

    //reverse the result
    reverse( ans.begin(), ans.end() );

    return ans;
}

\end{lstlisting}