\section{495 --- Teemo Attacking}
In LOL world, there is a hero called \textbf{Teemo} and his attacking can make his enemy \textbf{Ashe} be in poisoned condition. Now, given the Teemo's attacking ascending time series towards Ashe and the poisoning time duration per Teemo's attacking, you need to output the total time that Ashe is in poisoned condition.

You may assume that Teemo attacks at the very beginning of a specific time point, and makes Ashe be in poisoned condition immediately.

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: [1,4], 2

\textbf{Output}: 4

\textbf{Explanation}: 

At time point 1, Teemo starts attacking Ashe and makes Ashe be poisoned immediately. 

This poisoned status will last 2 seconds until the end of time point 2. 

And at time point 4, Teemo attacks Ashe again, and causes Ashe to be in poisoned status for another 2 seconds. 

So you finally need to output 4.
 
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: [1,2], 2

\textbf{Output}: 3

\textbf{Explanation}: 

At time point 1, Teemo starts attacking Ashe and makes Ashe be poisoned. 

This poisoned status will last 2 seconds until the end of time point 2. 

However, at the beginning of time point 2, Teemo attacks Ashe again who is already in poisoned status. 

Since the poisoned status won't add up together, though the second poisoning attack will still work at time point 2, it will stop at the end of time point 3. 

So you finally need to output 3.
\end{flushleft}
 

\paragraph{Note:}

\begin{itemize}
\item You may assume the length of given time series array won't exceed 10000.
\item You may assume the numbers in the Teemo's attacking time series and his poisoning time duration per attacking are non-negative integers, which won't exceed 10,000,000.
\end{itemize}

\subsection{Merge Overlap}
\begin{itemize}
\item Each time point $t$ is mapped to an interval $[t, t+d]$ where $d$ is the duration.
\item Since the end of intervals is already ascending, no need to sort first.
\item We check each interval's start time against current end time. If the start time is later than current end time, we know we this is a non-overlapped interval and we accumulated total time and update current start time.
\item We always update current end time as current interval's end time.
\end{itemize}

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Merge Interval}]
int findPoisonedDuration( vector<int>& timeSeries, int duration )
{
    if( timeSeries.empty() )
    {
        return 0;
    }

    int start = timeSeries[0];
    int end = start + duration;

    int ans = 0;

    for( size_t i = 1; i < timeSeries.size(); ++i )
    {
        if( timeSeries[i] > end )
        {
            //this is a non-overlapped interval
            //accumulate the total time
            ans += end - start;
            //update the start time of next non-overlapped
            //merged interval
            start = timeSeries[i];
        }

        //update current merged interval's end time.
        end = timeSeries[i] + duration;
    }

    //we have to add the final interval
    ans += ( end - start );

    return ans;
}
\end{lstlisting}