\section{604 --- Design Compressed String Iterator}
Design and implement a data structure for a compressed string iterator. It should support the following operations: \texttt{next} and \texttt{hasNext}.

The given compressed string will be in the form of each letter followed by a positive integer representing the number of this letter existing in the original uncompressed string.

\begin{itemize}
\item \texttt{next}: if the original string still has uncompressed characters, return the next letter; Otherwise return a white space.
\item \texttt{hasNext}: Judge whether there is any letter needs to be uncompressed.

\end{itemize}
\paragraph{Note:}

\begin{itemize}
\item Please remember to \texttt{RESET} your class variables declared in \texttt{StringIterator}, as static/class variables are persisted across multiple test cases.
\end{itemize}

\paragraph{Example:}
\setcounter{lstlisting}{0}

\begin{lstlisting}[style=customc]
StringIterator iterator = new StringIterator("L1e2t1C1o1d1e1");

iterator.next(); // return 'L'
iterator.next(); // return 'e'
iterator.next(); // return 'e'
iterator.next(); // return 't'
iterator.next(); // return 'C'
iterator.next(); // return 'o'
iterator.next(); // return 'd'
iterator.hasNext(); // return true
iterator.next(); // return 'e'
iterator.hasNext(); // return false
iterator.next(); // return ' '
\end{lstlisting}

\subsection{State Machine}
We can conclude that there are 3 kind of states for the iterator
\begin{itemize}
\item Count of current letter is zero
\item Count of current letter is non-zero
\item End of string.
\end{itemize}

For function \texttt{next}, we could have
\begin{itemize}
\item Count of current letter is zero and not at the end of string: we get next letter and its count, at the same time, move index to where a new letter is found or the end of string.
\item Count of current letter is non-zero: we output current letter and decrements the count.
\end{itemize}

For function \texttt{hasNext}, we have to check both conditions
\begin{itemize}
\item Count of current letter is zero or not
\item The index is at the end of string or not.
\end{itemize}
