\section{645 --- Set Mismatch}
The set $S$ originally contains numbers from 1 to $n$. But unfortunately, due to the data error, one of the numbers in the set got duplicated to another number in the set, which results in repetition of one number and loss of another number.

Given an array $A$ representing the data status of this set after the error. Your task is to firstly find the number occurs twice and then find the number that is missing. Return them in the form of an array.

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: $A = [1,2,2,4]$

\textbf{Output}: $[2,3]$
\end{flushleft}

\paragraph{Note:}

\begin{itemize}
\item The given array size will in the range [2, 10000].
\item The given array's numbers won't have any order.
\end{itemize}

\subsection{Index By Itself}
This approach has been appeared in previous problems. 

\begin{itemize}
\item Traverse the array, for each element $A[i]$, we multiply $A[A[i]-1]$ by $-1$. If $A[A[i]-1]$ is already a negative number, then the duplicate number is $A[i]-1$.
\item Traverse the array again, if an element, say $A[k]$ is larger than zero, $k+1$ is the missing number.
\end{itemize}

\subsection{XOR}
Consider an array $D$ with $n−1$ elements containing numbers from $1$ to $n$ with one number missing out of them. To find the missing one, we can take the XOR of all the elements of $D$ with all the numbers from $1$ to $n$. By doing so, we get the required missing number. This works because XOR of two same numbers are zero. Thus, only the number which is missing can't get canceled by XOR.

Now, By taking the XOR of all the elements of the given array $A$ with all the numbers from 1 to $n$, we will get a result, $z$, as \lstinline[language=Java, basicstyle=\small\ttfamily, keywordstyle=\bfseries\color{green!40!black}]|x ^ y|. Here, $x$ and $y$ refer to the repeated and the missing term in $A$.

Now, we'll get a 1 in the binary representation of $z$ only at those bit positions which have a 1 in either $x$ or $y$, and a 0 at the same bit position in the other one. For this problem, we consider the rightmost bit position, $b$, which is 1 in $z$, although any bit would work.

If we divide the elements of $A$ into two parts such that the first set contains the elements which have a 1 at bit position $b$ and the second set contains the elements having a 0 at the same position, we'll get $x$ from one set and $y$ from another. Thus, we test $1$ to $n$ and all elements in $A$ by checking their bit position $b$.

\begin{itemize}
\item XOR all the numbers with value 1 in the bit position $b$ to get a result $\alpha$.
\item XOR all the numbers with value 0 in the bit position $b$ to get a result $\beta$.
\end{itemize}

But, we don't know which one is missing and which one is duplicate. We have to iterate over $A$ again to check if $\alpha$ or $\beta$ appear in the array.
