\section{692 --- Top K Frequent Words}
Given a non-empty list of words, return the $k$ most frequent elements.

Your answer should be sorted by frequency from highest to lowest. If two words have the same frequency, then the word with the lower alphabetical order comes first.

\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: 

\fcc{["i", "love", "leetcode", "i", "love", "coding"]}, 

$k = 2$

\textbf{Output}: \fcc{["i", "love"]}

\textbf{Explanation}: \fcc{"i"} and \fcc{"love"} are the two most frequent words.

Note that \fcc{"i"} comes before \fcc{"love"} due to a lower alphabetical order.
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: 

\fcc{["the", "day", "is", "sunny", "the", "the", "the", "sunny", "is", "is"]}, 

$k = 4$

\textbf{Output}: \fcc{["the", "is", "sunny", "day"]}

\textbf{Explanation}: 

\fcc{"the"}, \fcc{"is"}, \fcc{"sunny"} and \fcc{"day"} are the four most frequent words, with the number of occurrence being 4, 3, 2 and 1 respectively.
\end{flushleft}

\paragraph{Note:}

\begin{itemize}
\item You may assume $ k $ is always valid, $1 \leq k \leq N$, where $N$ is number of unique elements.
\item Input words contain only lowercase letters.
\end{itemize}

\paragraph{Follow up:}

\begin{itemize}
\item Try to solve it in $ O(n log k) $ time and $ O(n) $ extra space.
\end{itemize}

\subsection{Heap}
This is a typical heap structure (priority queue) usage problem. When using \fcc{"C++ priority_queue"}, the ordering is defined as below
\begin{itemize}
\item The word with less appearances are put on the top of the queue.
\item If two words have same appearances, put the higher alphabetical order word on the top of the queue
\end{itemize}

We can lower the memory usage by using 

\fcc{"class string_view"}, 

and we can directly use the \fcc{"iterator"} of the hash map as the element of the queue.

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Heap}]
vector<string> topKFrequent( vector<string>& words, int k )
{
    using dict_type = unordered_map<string_view, int>;

    dict_type dict;

    //first count the appearances of each word
    for( const auto& word : words )
    {
        string_view sv( word );

        dict[word] += 1;
    }

    auto cmp = []( dict_type::iterator it1, dict_type::iterator it2 )
    {
        if( it1->second > it2->second )
        {
            //the less appearances will
            //on the top
            return true;
        }

        if( it1->second == it2->second )
        {
            //the higher alphabetical order word
            //will on the top
            return it1->first < it2->first;
        }

        return false;
    };

    //use iterator as the element of the queue
    priority_queue<dict_type::iterator, vector<dict_type::iterator>, decltype( cmp )> pq( cmp );

    for( auto it = dict.begin(); it != dict.end(); ++it )
    {
        pq.push( it );

        int n = static_cast< int >( pq.size() );

        if( n > k )
        {
            //remove the top
            pq.pop();
        }
    }

    vector<string> ans;
    ans.reserve( k );

    while( !pq.empty() )
    {
        auto it = pq.top();
        ans.emplace_back( it->first );
        pq.pop();
    }

    //since high alphabetical word is added first
    //we will reverse the result
    reverse( begin( ans ), end( ans ) );
    return ans;
}
\end{lstlisting}