\section{758 --- Bold Words in String}

Given a set of keywords \fcj{words} and a string $S$, make all appearances of all keywords in $S$ bold. Any letters between \fcj{<b>} and \fcj{</b>} tags become bold.

The returned string should use the least number of tags possible, and of course the tags should form a valid combination.

For example, given that \fcj{words = ["ab", "bc"]} and \fcj{S = "aabcd"}, we should return \fcj{"a<b>abc</b>d"}. Note that returning \fcj{"a<b>a<b>b</b>c</b>d"} would use more tags, so it is incorrect.

\paragraph{Note:}

\begin{enumerate}
\item \fcj{words} has length in range \fcj{[0, 50]}.
\item \fcj{words[i]} has length in range \fcj{[1, 10]}.
\item $S$ has length in range \fcj{[0, 500]}.
\item All characters in \fcj{words[i]} and $S$ are lowercase letters.
\end{enumerate}

\subsection{Brute Force}
We check for all occurrences of each word and mark the corresponding letters bold.

We maintain a boolean array \fcj{flags} and \fcj{flags[i] = true} if and only if the $i$-th letter is bold. For each starting position $i$ in $S$, and for each word, if \fcj{S[i]} starts with this word, we set the appropriate letters in $S$ as bold.

With generated \fcj{flags}, a letter in position $i$ is 

\begin{itemize}
\item the first bold letter of the group if \fcc{flags[i] && (i == 0 \|\| flags[i-1]==0)}, 
\item and is the last bold letter if \fcc{flags[i] && (i == N-1 \|\| flags[i+1]==0)}. 

\end{itemize}
Once we know which letters are the first and last bold letters of a group, we know where to put the \fcj{"<b>"} and \fcj{"</b>"} tags.

\setcounter{lstlisting}{0}
\begin{lstlisting}[style=customc, caption={Brute Force}]
string boldWords( vector<string>& words, string S )
{
    vector<unsigned char> flags( S.size(), 0 );
    string_view sv( S );
    for( size_t i = 0; i < S.size(); ++i )
    {
        for( const auto& word : words )
        {
            string_view svw( word );
            if( sv.substr( i, word.size() ) == svw )
            {
                //sv[i...i+word.size()-1]=word
                //mark flags[i,i+word.size()-1]
                //as bold letter flag
                auto b = flags.begin();
                advance( b, i );
                auto e = b;
                advance( e, word.size() );
                fill( b, e, 1 );
            }
        }
    }
    string ans;
    for( size_t i = 0; i < S.size(); ++i )
    {
        if( ( flags[i] == 1 ) && ( ( i == 0 ) || ( flags[i - 1] == 0 ) ) )
        {
            //the start of bold letter
            ans += "<b>";
        }
        ans.push_back( S[i] );
        if( ( flags[i] == 1 ) && ( ( i == ( S.size() - 1 ) ) || ( flags[i + 1] == 0 ) ) )
        {
            //the end of bold letter
            ans += "</b>";
        }
    }
    return ans;
}
\end{lstlisting}