\section{782 --- Transform to Chessboard}
An $N \times N$ \fcj{board} contains only 0s and 1s. In each move, you can swap any 2 rows with each other, or any 2 columns with each other.

What is the minimum number of moves to transform the board into a \textit{chessboard} --- a board where no 0s and no 1s are 4-directionally adjacent? If the task is impossible, return $-1$.

\paragraph{Examples:}
\begin{flushleft}
\textbf{Input}: \fcj{board = [[0,1,1,0],[0,1,1,0],[1,0,0,1],[1,0,0,1]]}

\textbf{Output}: 2

\textbf{Explanation}:

One potential sequence of moves is shown below, from left to right:

\fcj{0110     1010     1010}

\fcj{0110 --> 1010 --> 0101}

\fcj{1001     0101     1010}

\fcj{1001     0101     0101}

The first move swaps the first and second column.

The second move swaps the second and third row.

\textbf{Input}: \fcj{board = [[0, 1], [1, 0]]}

\textbf{Output}: 0

\textbf{Explanation}:

Also note that the board with 0 in the top left corner,

\fcj{01}

\fcj{10}

is also a valid chessboard.

\textbf{Input}: \fcj{board = [[1, 0], [1, 0]]}

\textbf{Output}: $-1$

\textbf{Explanation}:

No matter what sequence of moves you make, you cannot end with a valid chessboard.


\end{flushleft}
\paragraph{Note:}

\begin{itemize}
\item \fcj{board} will have the same number of rows and columns, a number in the range \fcj{[2, 30]}.
\item \fcj{board[i][j]} will be only 0s or 1s.
\end{itemize}

\subsection{Dimension}
In a valid chess board, the adjacent cells are different colors. These means, in each row and column, ones and zeros are shown in alternate order. Another property is that these rows or columns must have had half zeros and half ones, (except when the length is odd, where there could be an extra zero or one).

Furthermore, because \textbf{a row move followed by a column move is the same as a column move followed by a row move}, we can assume all the row moves happen first, then all the column moves.  (Note: it is \textit{not} true that move row $i$ then $j$ is same as moving row $j$ then $i$.)

For example, assume we have an array \fcj{[0, 1, 1, 1, 0, 0]} and the problem is to know the minimum moves to change to 0/1 alternate pattern, i.e., \fcj{[0, 1, 0, 1, 0, 1]} or \fcj{[1, 0, 1, 0, 1, 0]}.