\section{847 --- Shortest Path Visiting All Nodes}

\textbf{Hard}

An undirected, connected graph of $N$ nodes (labeled 0, 1, 2, $\ldots$, $N-1$) is given as graph.

\fcj{graph.length = N}, and $j \neq i$ is in the list \fcj{graph[i]} exactly once, if and only if nodes $i$ and $j$ are connected.

Return the length of the shortest path that visits every node. You may start and stop at any node, you may revisit nodes multiple times, and you may reuse edges.

 
\paragraph{Example 1:}

\begin{flushleft}
\textbf{Input}: \fcj{[[1,2,3],[0],[0],[0]]}

\textbf{Output}: 4

\textbf{Explanation}: One possible path is \fcj{[1,0,2,0,3]}
\end{flushleft}

\paragraph{Example 2:}

\begin{flushleft}
\textbf{Input}: \fcj{[[1],[0,2,4],[1,3,4],[2],[1,2]]}

\textbf{Output}: 4

\textbf{Explanation}: One possible path is \fcj{[0,1,4,2,3]}

\end{flushleft}
 

\paragraph{Note:}

\begin{itemize}
\item $ 1 \leq \texttt{graph.length} \leq 12 $
\item $ 0 \leq \texttt{graph[i].length} < \texttt{graph.length} $
\end{itemize}

\subsection{BFS}
The number of nodes are less than 13, so we can use a bit mask to represent the visit status of each node starting from one node.

starting from each node, we can store the visited nodes on the path into a state variable. If we visit a node labeled $k$, we set the $k$th bit of state associated with the starting node as 1.

During the BFS process, if we find a state with all bits are set, we know the shorted path length is found

\setcounter{lstlisting}{0}
\lstinputlisting[style=customc, caption={BFS}]{847_BFS.cpp}

\subsection{Dynamic Programming}
Similar to \textbf{Bellman-Ford} algorithm. 

In this approach, we iterate all states and update the distance by selecting each node as the start of a path. 

Care must be taken to when a next state is found to be equal to current state. In this scenario, we need to run the above iteration loop again because a minimum state might only be achieved through multiple steps through some path. 

\setcounter{lstlisting}{0}
\lstinputlisting[style=customc, caption={DP}]{847_DP.cpp}